---
title: "**Travor's Dice Problem**"
author: "Gwendolin Lüdtke, Sina Spors"
date: "13.11.2018"
output:
  html_document:
    highlight: textmate
    code_folding: show
    theme: spacelab
    toc: true 
    toc_float: 
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### **Probability as likelyhood**

*Tsunami scientist Trevor rolls some dice and tells you that the
added result is 17. How many dice did Trevor roll?*

To solve this problem of Trevor, a simulation of rolling the dices should be carried out.

We can solve this problem in several ways. Here you can see a possible approach:

First of all, in order to create a more flexible code, variables instead of numbers are used for the minimum and maximum number of dices as well as for the number of tests. 
The number of tests should be high to ensure high reliability. Moreover, a vector (x) of the length n is generated by using the ```rep()``` command.


```{r}

# Minimum number of dices 
min_dice <- 3 
# Maximum number of dices
max_dice <- 17 
n <- 10000
x <- rep(NA,n)
```


After the declaration and initialisation of the variables, ```for-loops``` are used to simulate the repition of throwing 3 to 17 dices a certain number of times. It must be noted that the number of eyes on the dice must be added together. this can be achieved with the ```sum``` -function.

```{r}
# Repeat this loop n-times
for (y in 1:n){ 
# Number of the dices
  for (i in min_dice:max_dice) { 
    s <- sum(sample(1:6,i,replace=TRUE))
  
  if (s==17)  {
    x[i+y] <- i 
    }
  }
}
    
```


### **Creating a Plot**

For a better view, a histogram can be made. By defining the axis boundaries, a precise view of the concrete value range of the experiment can be created.

It is clear from the diagram that it is most likely to roll a 17 when using 5 dices. With 6 and more dices it is noticeable that it's increasingly unlikely to roll a 17.

```{r}
hist(x,
     main = "Travor's dice problem",
     xlab = "Number of dice",
     col  = "blue",
     ylab = "Number of experiemnts",
     xlim = c(2,9),
     ylim = c(0,1000))
```




